%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry%
    {Programming Analyst for Quality Assurance} % Job title
    {UC Irvine Office of Information Technology} % Organization
    {} % Location
    {May. 2016 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Create, develop, and maintain innovative testing frameworks %
        for testing development, staging, and production environments as well %
        as lead code reviews during sprints.}
        \item {Develop frameworks, all written in Java and open-source on GitHub, %
        that range from a completely data driven plugin based testing suite to a %
        code-only replacement to Apache jMeter.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry%
    {Co-Founder \& Lead Developer} % Job title
    {Cryptix} % Organization
    {} % Location
    {Aug. 2014 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A collaborative hobby development team working on games and %
        applications for mobile, desktop, and virtual reality marketplaces.}
        \item {Current projects include universal virtual driver, a mobile %
        streaming application, and games with a focus on procedural generation %
        and virtual reality.}
        % \item {A collaborative team working on games and applications for %
        % mobile, desktop, and VR marketplaces. Current development projects range %
        % from an experimental software driver to allow direct communication %
        % between devices regardless of platform, a mobile streaming application, %
        % and experimental desktop games with a focus on procedural generation and %
        % virtual reality.}
      \end{cvitems}
    }

  %---------------------------------------------------------
    \cventry%
      {Investment Consultant} % Job title
      {Mechler Group} % Organization
      {} % Location
      {Nov. 2013 -- Aug. 2014} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Remotely provided information about cryptographic currency and %
          developed custom cryptographic mining and management software.}
          \item {Worked with investors to provide information, %
          hardware systems, and custom software to meet their individual needs %
          and desires.}
        \end{cvitems}
      }

%---------------------------------------------------------
  \cventry%
    {Co-Owner \& Head of Network Management} % Job title
    {Aegis Gaming} % Organization
    {} % Location
    {Jun. 2010 -- Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and maintained Windows and Linux based servers remotely. %
        Developed custom shell and bash scripts to automate server maintenance. %
        Network averaged around 75,000 unique users a month.}
        \item {Recruited and trained 50+ staff in basic Java programming and %
        use of Linux Shell.}
        \item {Created custom server software to better manage the network's %
        traffic and support unique server requirements. This ranged from %
        wrappers for existing software that modified packets on the fly to %
        standalone software written ground up (Java and C++ were the primary %
        languages used).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
